Unfolding the City: Spatial Preference Based on Individual Demographic Characteristics

### 2020-01-09 ia/ia_vis_3d.tex
new version

In this work, we perform the survey in Shenzhen, which is one of the most modern metropolis in China. The experiment is deployed on Wechat, the most widely used social media mobile application in China. Fig. \ref{fig:app} shows \colorbox{yellow}{the interfaces of survey app.} For privacy issue, all detailed personal information are desensitized to categorical levels. Considering the main aim on the relationship between spatial preference and demographic characteristics, two crucial aspects need to be collected:

@@

\begin{figure}
 \centering
 \includegraphics[width=9cm]{pictures/survey_app}
  \captionsetup{justification=centering}
 \caption{Census Interface: (a) personal characteristics collecting page; (b) trips collecting page; (c) credit system page.}
 \label{fig:app}
\end{figure}

@@

Over the releasing time period from 2015-11 to 2016-01, 21,435 individuals participated in the census and 229,155 trips were collected. \colorbox{yellow}{Each volunteer contributed 11 trips average.}

@@

Our case-study data is confined to a small proportion of Wechat users who opt to contribute their demographic profiles and movements.
Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of the population in the city.

Fig. \ref{fig:data_age_edu} gives the distribution of gender, age and education over the population. For participated citizens, 48\% of them are female and 52\% are male. It is consistent with governmental statistics that 47\% of the whole citizens are female and 53\% are male\footnote{http://tjj.sz.gov.cn/zwgk/zfxxgkml/tjsj/tjgb/201804/t20180427\_11800902.htm}. The age collected covers a wide range, dominating between 18 and 45. There are also records pertaining to individuals below the age of 18 or above 70. According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. The age distribution in collected data follows the fact that Shenzhen is a city where the majority is young. Fig, \ref{fig:data_age_edu}(b) gives the distribution of education levels, ranging from low to high. The technical college and university dominate the samples at the 61\% occupancy rate. Fig. \ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, businessmen and so on. \colorbox{yellow}{Fig. \ref{fig:data_job_inc}(b) gives the radar diagram of the annual pay.} The majority get paid below 200,000. Citizens with higher salary are also reached in our census.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data2}
 \caption{Job and Income Distribution: (a) job; (b) income}
 \label{fig:data_job_inc}
\end{figure}

The basic statistics related to movements are shown in Fig. \ref{fig:data_geometry}. \colorbox{yellow}{Fig. ~\ref{fig:data_geometry}(a) visualizes the distribution of trip quantity of each citizen. It has a heavy-tail trait, which follows the law of most human-related statistics}. In Fig. ~\ref{fig:data_geometry}(b), the active traveling time (here, we take the start time as the representative of active time) follows the common knowledge about urban life. There are obvious morning and evening rush hours. Fig. ~\ref{fig:data_geometry}(c) gives the counting of different traveling purposes. 95\% trips are tagged with clear raveling purpose in the data. 33\% are going home and 37\% are going to work. Besides this kind of routine traveling, there are also substantial trips such as going shopping, going the hospital, etc. Fig. ~\ref{fig:data_geometry}(d) shows the spatial distribution of the origins and destinations. It is found that more dots are located in Futian and Nanshan districts, the city's heart than the surrounding areas. This is consistent to Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data3}
 \caption{Statistics of Trips: (a) distribution of trip quantity of each citizen; (b) start time of trips; (c) purpose of trips; (d) distribution of origins/destinations. }
 \label{fig:data_geometry}
\end{figure}

Due to lacking of governmental statistics, we cannot verify all characteristics and movements collected are consistent with all the citizens in Shenzhen. From the perspective of survey, there is always inevitable bias inherent in fully representing the ground truth of the population. However, the preliminary statistical analysis shows the rich scope of the data, which embodies positive sign of a relatively even sampling of the population.

@@

\begin{figure*}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=18.1cm]{pictures/teaser.eps}
 \caption{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) a t-SNE visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) data-driven profiles support users with organic individual perception; (d) group of interested individuals can be saved; (e) movement of the chosen group is visualized and explored in 2.5D main view; (f) a dock is provided to restore and compare findings; (g) different choices of 2.5D encoding can be selected.}
 \label{fig:teaser}
\end{figure*}

>>>>

In this work, we perform the survey in Shenzhen, which is one of the most modern metropolis in China. The experiment is deployed on Wechat, the most widely used social media mobile application in China. Fig. \ref{fig:app} shows the interfaces of survey app. For privacy issue, all detailed personal information are desensitized to categorical levels. Considering the main aim on the relationship between spatial preference and demographic characteristics, two crucial aspects need to be collected:

@@

\begin{figure}
 \centering
 \includegraphics[width=9cm]{pictures/survey_app_eng}
  \captionsetup{justification=centering}
 \caption{Census app interface: (a) personal characteristics collecting page; (b) trips collecting page; (c) credit system page. (In real census survey, contents are shown in Chinese.)}
 \label{fig:app}
\end{figure}

@@

Over the releasing time period from 2015-11 to 2016-01, 21,435 individuals participated in the census and 229,155 trips were collected.

Our case-study data is confined to a small proportion of Wechat users who opt to contribute their demographic profiles and movements. Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics. In Fig.\ref{fig:data_overview}, population distribution of each characteristic is shown. The length of the block is coded for population quantity.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data_overview}
 \caption{Preliminary statistics of each characteristic in collected demographic data.}
 \label{fig:data_overview}
\end{figure}

From the figure, 51.2\% of the participated citizens are male and 48.8\% are female. It is consistent with governmental statistics that 47\% of the whole citizens are female and 53\% are male\footnote{http://tjj.sz.gov.cn/zwgk/zfxxgkml/tjsj/tjgb/201804/t20180427\_11800902.htm}. The age collected covers a wide range, dominating between 18 and 45. There are also records pertaining to individuals below the age of 18 or above 70. According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. The age distribution in collected data follows the fact that Shenzhen is a city where the majority is young. From the distribution of education levels, ranging from low to high. The technical college and university dominate the samples at the 61\% occupancy rate. The majority get paid below 200,000. Citizens with higher salary are also reached in our census. Due to lacking of governmental statistics, we cannot verify all characteristics collected are consistent with all the citizens in Shenzhen. From the perspective of survey, there is always inevitable bias inherent in fully representing the ground truth of the population. However, the preliminary statistical analysis shows the rich scope of the data, which embodies positive sign of a relatively even sampling of the population in the city.

\iffalse
Fig. \ref{fig:data_age_edu} gives the distribution of gender, age and education over the population. For participated citizens, 48\% of them are female and 52\% are male. It is consistent with governmental statistics that 47\% of the whole citizens are female and 53\% are male\footnote{http://tjj.sz.gov.cn/zwgk/zfxxgkml/tjsj/tjgb/201804/t20180427\_11800902.htm}. The age collected covers a wide range, dominating between 18 and 45. There are also records pertaining to individuals below the age of 18 or above 70. According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. The age distribution in collected data follows the fact that Shenzhen is a city where the majority is young. Fig, \ref{fig:data_age_edu}(b) gives the distribution of education levels, ranging from low to high. The technical college and university dominate the samples at the 61\% occupancy rate. Fig. \ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, businessmen and so on. \colorbox{yellow}{Fig. \ref{fig:data_job_inc}(b) gives the radar diagram of the annual pay.} The majority get paid below 200,000. Citizens with higher salary are also reached in our census.

@@

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data2}
 \caption{Job and Income Distribution: (a) job; (b) income}
 \label{fig:data_job_inc}
\end{figure}
\fi

The basic statistics related to movements are shown in Fig. \ref{fig:data_geometry}. Fig. ~\ref{fig:data_geometry}(a) visualizes the distribution of trip quantity of each citizen. It has a heavy-tail trait, which follows the law of most human-related statistics. In Fig. ~\ref{fig:data_geometry}(b), the active traveling time (here, we take the start time as the representative of active time) follows the common knowledge about urban life. There are obvious morning and evening rush hours. Fig. ~\ref{fig:data_geometry}(c) gives the counting of different traveling purposes. 95\% trips are tagged with clear raveling purpose in the data. 33\% are going home and 37\% are going to work. Besides this kind of routine traveling, there are also substantial trips such as going shopping, going the hospital, etc. Fig. ~\ref{fig:data_geometry}(d) shows the spatial distribution of the origins and destinations. It is found that more dots are located in Futian and Nanshan districts, the city's heart than the surrounding areas. This is consistent to Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data3_2}
 \caption{Statistics of Trips: (a) distribution of trip quantity of each citizen; (b) start time of trips; (c) purpose of trips; (d) distribution of origins/destinations. }
 \label{fig:data_geometry}
\end{figure}

@@

\begin{figure*}[htb!]
 \centering
 \includegraphics[width=18.1cm]{pictures/teaser.eps}
 \caption{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) a t-SNE visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) data-driven profiles support users with organic individual perception; (d) group of interested individuals can be saved; (e) movement of the chosen group is visualized and explored in 2.5D main view; (f) a dock is provided to restore and compare findings; (g) different choices of 2.5D encoding can be selected.}
 \label{fig:teaser}
\end{figure*}
